Experiences in teaching with Jupyter, Jupyterhub, and nbgrader

### 2020-01-05 paper/paper.tex
some manuscript edits ...

At the University of Silesia Python used to be a a first programming
language for students of Applied Computer Science. There has beem
implemented a concept of ``mobile computer classroom'' which consists
of inexpensive and mobile computers which are are available to
students in the rental office. Initially it consisted of 10-inch
netbooks, currently the hardware is based on Chromebooks which are
very easy to maintain. Therefore an important aspect is the
accessibility of the work environment in a web browser. Jupyter
notebook fits perfectly in such a scenario. In recent years several
work scenarios based on Juyter notebook have been developed in such an
environment.

Here, we will mainly concentrate on the case of course ``Introduction
to Artifitial Intelligence``, which is attented by c.a. 50 students
every year. The course used Jupyter notebook as a teaching tool during
the lectures and tutorials. Students had to submit their work in the
form of notebooks form. Additionally automating testing software has been 
used to help both students as well as teachers.

@@

Jupyterhub a software providing a way to serve Jupyter notebook for
multiple users. It can be used in a classes of students, all

 a centrally provided resource to run a Jupyter notebook from a
remote computer makes problem sets or more generally teaching material easily
accessible without the need for a local Python installation. Furthermore, this
approach ensures a consistent working environment for all students. However,
it might be an important experience for students that all work which they
are doing could in fact be done on their own computer instead of using some
remote service where the underlying machinery is completely hidden.

@@

\bibitem{nbgrader}
% https://doi.org/10.21105/jose.00032 
Project Jupyter, Blank, D., Bourgin, D., Brown, A., Bussonnier, M.,
Frederic, J., Granger, B., Griffiths, T. L.,  Hamrick, J., Kelley, K.,
Pacer, M., Page, L., P{\'e}rez, F., Ragan-Kelley, B., Suchow, J. W.,
\& Willing, C. (2019).
nbgrader: A Tool for Creating and Grading Assignments in the Jupyter Notebook,
\textit{Journal of Open Source Education}, 2(11), 32.
% Format for books
%\bibitem{RefB}
%Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

>>>>

At the University of Silesia, Python is used as a introductory
programming language for students of Applied Computer Science. There
has been implemented a concept of ``mobile computer classroom'' which
consists of inexpensive and mobile thin-client computers which are are
available to students in the rental office. They are used to access
compute resources where the required software is available.
Chromebooks currently play the role of thins clients, which is why all
services must be available through a web browser.  Jupyter notebook
fits perfectly in such a scenario. In recent years several work
scenarios based on Juyter notebook have been developed in such an
environment.

In the Institute of Physics, the widespread use of the Python-based
computer algebra system SageMath\cite{sagemath} system available in
the browser been started for several years. This turned out to be a
excellent solution. The Sage notebook (\texttt{sagenb}) provided
ubiquitous access to computations in science education, and a large
number of teaching materials where produced. This technology was also
replicated in partner high schools as part of the iCSE4school project
(details see \cite{icse4school}). Since 2011, c.a. 2000 students and
over 500 high school pupils have used the system. The Sage notebooks
were served using a small computer cluster and until today users
created around 30000 notebook documents which generated in peak time
over computation per second.

The notebook system \texttt{sagenb} became obsolete and the currently
SageMath switched to the Jupyter notebook. Additionally, Jupyter
notebook supports using many other programming languages. Therefore en
effort was initiated to replace old \texttt{sagenb} notebooks system
for the sake of Jupyter, and to expand this technology to other
teaching programmes.

In this paper, we will mainly concentrate on the case of course
``Introduction to Artificial Intelligence``, which is attended by
c.a. 50 Applied Computer Science students every year. The course uses
Jupyter notebook as a teaching tool during both the lectures and
tutorials. Students had to submit their work in the form of notebooks
using \texttt{nbgrader} software. Their work used automated testing to
help both students as well as teachers.

@@

Jupyterhub a software providing a way to serve Jupyter notebook for
multiple users. It can be used in a single classes of students, or can
be deployed centrally on a faculty level. In both cases it provides
computational resources to run a Jupyter notebook from a remote
computing center. It can be used to distribute problem sets or more
generally teaching material easily. and without the need for a local
Python installation. Furthermore, this approach ensures a consistent
working environment for all students.

However, it might be an important experience for students that all
work which they are doing could in fact be done on their own computer
instead of using some remote service where the underlying machinery is
completely hidden.

@@

\bibitem{nbgrader}
% https://doi.org/10.21105/jose.00032 
Project Jupyter, Blank, D., Bourgin, D., Brown, A., Bussonnier, M.,
Frederic, J., Granger, B., Griffiths, T. L.,  Hamrick, J., Kelley, K.,
Pacer, M., Page, L., P{\'e}rez, F., Ragan-Kelley, B., Suchow, J. W.,
\& Willing, C. (2019).
nbgrader: A Tool for Creating and Grading Assignments in the Jupyter Notebook,
\textit{Journal of Open Source Education}, 2(11), 32.
% Format for books
%\bibitem{RefB}
%Author, Book title, page numbers. Publisher, place (year)
% etc

\newcommand{\etalchar}[1]{$^{#1}$}
\bibitem{sagemath}
\emph{{S}ageMath, the {S}age {M}athematics {S}oftware {S}ystem ({V}ersion
  8.9.0)}, The Sage Developers, 2019, {\tt https://www.sagemath.org}.

\bibitem{icse4school}
  Science education with computational perspective - a project funded by grant from: Erasmus+ Programme 
 \texttt{http://visual.icse.us.edu.pl/methodology}

\end{thebibliography}
